\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright
\usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse}
}

\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
	{\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
	\vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {#1}}\\
		#2 \\ #3
	\end{center}
	\vspace*{-8pt}
}

\newenvironment{achievements}{
	\begin{list}
		{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
	\end{list}
}

\newcommand{\schoolwithcourses} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
	\vspace*{5pt}
}

\newcommand{\school} [4] {
	\textbf{#1} #2 $\bullet$ #3\\
	#4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\vspace*{-40pt}
	
	
	
	%==== Profile ====%
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {Daniel Chahine}}\\
		Toronto, ON $\cdot$ Chahinedaniel0@gmail.com $\cdot$ (416) 209-2420\\
	\end{center}
	
	%==== Education ====%
	\header{Education}
	\textbf{York University}\hfill North York, ON\\
	Honours Bachelor of Science: Computer Science \hfill Sept 2022 - April 2026 (Expected)\\

	\begin{itemize} \itemsep 0pt
		\item \textbf{Relevant Courses}: Advanced Object Oriented Programming, Software Tools, Theory of Computation, Calculus I \& II.
	\end{itemize}
	\hspace{21pt}
	 An overall GPA of 8.1/9 (A+)
	\vspace{2mm}
	
	%==== Experience ====%
	\header{Work Experience}
	\vspace{1mm}
	
	\textbf{Self Employed} \hfill Toronto, ON\\
	\textit{Online \& In-Person Tutor} \hfill Feb 2020 - Sept 2023\\
	\vspace{-1mm}
	\begin{itemize} \itemsep 1pt
		\item Offering personalized tutoring sessions in a variety of high school subjects including but not limited to Computer Science, Calculus, Advanced Functions, Robotics, Physics, Chemistry, and French.
		\item The role also involves actively promoting my services through online ads on Kijiji to attract and engage students.
	\end{itemize}
	
	%==== Projects ====%
	\header{Projects}
	\hspace{-3mm}
	{\textbf{Mind Maze \textbar{}}} {\sl Python, PyGame} \\
		An educational game that transforms learning into a journey. It merges education and entertainment, offering a program where players tackle maze challenges in mathematics, logic, and computer science.\\
	\vspace*{2mm}
	\hspace{-3mm}
	{\textbf{Platformer \textbar{}}} {\sl Python, PyGame, Game Development} \\
	A 2D role playing-game with the goal to explore various levels, collect fruits, and avoid traps. Different characters, challenging worlds, variety of backgrounds, animations, and a score mechanism. are implemented\\
	\vspace*{2mm}
	\hspace{-3mm}
	{\textbf{UNHack 2023 Presentation \textbar{}}} {\sl HTML, CSS, JavaScript} \\
	A website presenting an AI project to solve educational problems. The proposed solutions include an AI teaching assistant, and AI generation of personalized quizzes and assessment with different learning styles.\\
	\vspace*{2mm}
	\hspace{-3mm}
	{\textbf{Snake \textbar{}}} {\sl Python, PyGame} \\
	Recreated the Snake Game with new various themes and visuals.\\
	\vspace*{2mm}
	\hspace{-3mm}
	{\textbf{Pong \textbar{}}} {\sl Python, PyGame} \\
	Created the Pong Game using Python and allowing multiplayer players to play the game at once.\\
	\vspace*{2mm}
	\hspace{-3mm}
	{\textbf{Flappy Bird \textbar{}}} {\sl Python, PyGame} \\
	Recreated Flappy Bird with different themes and sounds effects using Python\\
	\vspace*{2mm}
	
	\header{Skills \& Rewards}
	\begin{tabular}{ l l }
		\vspace{1mm}
		&\textbf{Languages:} Java, Python, C, C\#, HTML, CSS, JavaScript, LaTeX \\
		\vspace{1mm}
		&\textbf{Trilingual:} English, French, Arabic \\
		&\textbf{Rewards:} Annual Lassonde Scholarship 2022 \& 2023 (4000\$x2), St George Antiochian Orthodox Church \\
		\vspace{1mm}
		&\hspace{16.5mm} Yearly Scholarship 2022 \& 2023(1000\$x2)\\
		&\textbf{Other Skills:} Game Development, Project Management, Teaching and Mentoring \\
	\end{tabular}
	\vspace{2mm}
	
	\header{Volunteer}
	\textbf{Jarvis Consulting Group} \hfill Student Ambassador\\
	Jarvis is an IT Company that provides with ongoing partnerships across North America\textquotesingle{}s top financial institutions, consulting firms, startups, and major technology companies. \hfill April 2023 - Present\\
	\vspace*{2mm}
	\textbf{SOYO Leader} \hfill Society of Orthodox Youth Organizations (SOYO)\\
	Served as a member of the Teen SOYO (Society of Orthodox Youth Organizations) in Montreal between 2018 and 2020, and continued in this role as a leader in Toronto since 2020. Actively participated in event planning. Organized sleepovers. Adeptly managed groups of children. \hfill Sep 2018 - Present\\
	\vspace*{2mm}
	\textbf{Summer Camp Counselor} \hfill Camp Transfiguration\\
	Worked at Camp Transfiguration, a 2-week overnight summer camp in Quebec. 2 weeks during August 2022 \& 2 weeks during 2023. Led and facilitated activities for children ages 8-17, including sports, arts and crafts, and team-building exercises. Provided emotional support and guidance to campers, ensuring a positive experience. Maintained accurate camper records and communicated effectively with parents and guardians.\\
	
	\ 
\end{document}